\chapter{Introduction}
\label{cha:Introduction}

DynamoDB is a fast and flexible NoSQL database service provided by Amazon Web Services\footnote{AWS is a comprehensive, evolving clout computing platform provided by Amazon.com, for further informations have a look at \href{https://aws.amazon.com}{www.aws.amazon.com}} and therefore is non-relational. It is a fully managed cloud service and supports both document and key-value store models. \cite{techtarget} \\

Without the user having to care for the management of his database, DynamoDB scales throughput capacity automatically to meet workload demands and partitions (and re-partitions) the data when the size table is growing, while synchronously replicating data across three facilities in an AWS Region, to enable high availability and data-durability. \\

Amazon DynamoDB makes it easy and cost-effective to store and retrieve any amount of data, while also serving any level of request traffic. Its data items are stored on solid-state drives providing high I/O performance, and can therefore efficiently handle high-scale requests. AWS user can interact with the service by using the AWS Management Console or a DynamoDB API. \\

This NoSQL database service allows documents, graphs and columnar among its data models. Its users can interact with it via GET and PUT queries after having stored their data in DynamoDB tables. In Addition, DynamoDB also supports basic CRUD operations and conditional operations.\\

DynamoDB can be used for nearly everything. For example for mobile, web, gaming, ad tech, IoT, etc.\\
